### 2018-03-16 paper/2-background.tex

We summarise differences between four discussed build systems in
Table~\ref{tab-summary}. The `Metadata' column refers to the \emph{auxiliary
build information} persistently stored between builds by all build systems:
\begin{itemize}
    \item \Make stores file modification times, or rather, it relies on the file
    system to do that. In principle a single \emph{dirty bit} per file is
    sufficient, as will be demonstrated in~\S\ref{sec-implementations}.
    \item \Excel stores one dirty bit per cell and the calculation chain from
    the previous build.
    \item \Shake stores the dependency graph discovered in the previous build,
    annotated with file content hashes for efficient checking of file changes.
    \item \Bazel stores all dependency graphs discovered in previous builds
    annotated with file hashes, and the content-addressable cache.
\end{itemize}

\begin{table}[h]
\vspace{-2mm}
\smaller
\centering
\begin{tabular}{l||l|l||l|c|c|c}
\hline
$\!$Build system$\!$& Metadata                       & Algorithm    & Dependencies & Minimal & Cutoff & Cloud$\!$\\\hline
$\!$\Make       $\!$& File modification times        & Topological  & Static       & Yes     & No     & No   $\!$\\
$\!$\Excel      $\!$& Dirty cells, calculation chain & Reordering   & Dynamic      & No      & No     & No   $\!$\\
$\!$\Shake      $\!$& Previous dependency graph      & Recursive    & Dynamic      & Yes     & Yes    & No   $\!$\\
$\!$\Bazel      $\!$& All dependency graphs, cache   & Topological  & Static       & Yes     & Yes    & Yes  $\!$\\\hline
\hline
\end{tabular}
\vspace{0.5mm}
\caption{Summary of build system differences.\label{tab-summary}}
\vspace{-8mm}
\end{table}

>>>>

We summarise differences between four discussed build systems in
Table~\ref{tab-summary}. The column \emph{`persistent build information'} refers
to the information that build systems persistently store between builds:
\begin{itemize}
    \item \Make stores file modification times, or rather, it relies on the file
    system to do that. In principle a single \emph{dirty bit} per file is
    sufficient, as will be demonstrated in~\S\ref{sec-implementations}.
    \item \Excel stores one dirty bit per cell and the calculation chain from
    the previous build.
    \item \Shake stores the dependency graph discovered in the previous build,
    annotated with file content hashes for efficient checking of file changes.
    \item \Bazel stores all dependency graphs discovered in previous builds
    annotated with file hashes, and the content-addressable cache.
\end{itemize}

\begin{table}[h]
\vspace{-2mm}
\smaller
\centering
\begin{tabular}{l||l|l||l|c|c|c}
\hline
$\!$Build system$\!$& Persistent build information   & Algorithm    & Dependencies & Minimal & Cutoff & Cloud$\!$\\\hline
$\!$\Make       $\!$& File modification times        & Topological  & Static       & Yes     & No     & No   $\!$\\
$\!$\Excel      $\!$& Dirty cells, calculation chain & Reordering   & Dynamic      & No      & No     & No   $\!$\\
$\!$\Shake      $\!$& Previous dependency graph      & Recursive    & Dynamic      & Yes     & Yes    & No   $\!$\\
$\!$\Bazel      $\!$& All dependency graphs, cache   & Topological  & Static       & Yes     & Yes    & Yes  $\!$\\\hline
\hline
\end{tabular}
\vspace{0.5mm}
\caption{Summary of build system differences.\label{tab-summary}}
\vspace{-8mm}
\end{table}
